Model Checking Differentially Private Properties

### 2018-01-29 main.tex
structures and some examples
more changes ;)
examples
remove product mdp from figure
use Times font to get more space
some changes
small changes

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{xspace}
\pagestyle{plain}
\usepackage{algorithm,algpseudocode}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{mathtools}
\usepackage{tikz}
\usepackage{url}
\usetikzlibrary{arrows,calc}

@@

\begin{abstract}
  We introduce the branching time temporal logic \dpCTL for specifying
  differential privacy. Its model checking algorithm is also developed. 
\end{abstract}

@@

\section{Examples}
\label{section:examples}
\input{examples}

\section{The Logic $\dpCTL$}
\label{section:dpCTL}
\input{dpCTL}

@@

\section{Model Checking Algorithms}
\label{section:model-checking-algorithms}
\input{algorithms}

\section{Applications}
\label{section:applications}
\input{applications}

>>>>

\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{xspace}
\pagestyle{plain}
\usepackage{algorithm,algpseudocode}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{wrapfig}
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{arrows,calc}
\usepackage{url}
\usepackage{times}

@@

\begin{abstract}
  We introduce the branching time temporal logic $\dpCTLstar$ for
  specifying differential privacy. Several differentially private
  mechanisms are formalized as Markov chains or Markov decision
  processes. Using our formal models, subtle privacy conditions
  are specified by $\dpCTLstar$. In order to verify privacy properties
  automatically, the model checking problems are investigated.  We
  give a model checking algorithm for Markov chains. Model checking
  $\dpCTLstar$ properties on Markov decision processes however is
  shown to be undecidable.
\end{abstract}

@@

\section{Markov Chains  for Differentially Private Mechanisms}
\label{section:examples}
\input{examples}

\section{The Logic $\dpCTLstar$}
\label{section:dpCTL}
\input{dpCTL}

@@

\section{Specifying Properties in $\dpCTLstar$}
\label{section:specifying-properties}
\input{specifications}

\section{Markov Decision Processes}
\label{section:mdp}
\input{mdp}

%\section{Model Checking Algorithms}
%\label{section:model-checking-algorithms}
%\input{algorithms}

\subsection{MDPs for Streaming Processes}
\label{section:applications}
\input{applications}
